---
title: "Assignment 4: Writing functions"
author: "Your Name"
date: "Today's date"
output: html_document
---

**Due Sunday, November 16, 2025 @ 11:59pm through Github**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

(1) Write a function called `mean_ci()` for computing 95% confidence intervals for either a single mean or a difference in means.

```{r}
#Put your code to read in the data here

```

If you would like a way to check that your confidence intervals are correct, here is the code I will use to check that your function works appropriately:
```{r echo = TRUE, eval = FALSE}
set.seed(8675309)
x <- rnorm(50)
y <- rnorm(30)

mean_ci(x)   # should get [1] -0.1404677  0.3458514

mean_ci(x, y, type="two.means")   # should get [1] -0.1875458  0.7320355

# checking the na.rm piece
x2 <- c(x, NA)
y2 <- c(y, NA)
mean_ci(x2, y2, type="two.means")  # should get [1] NA NA
mean_ci(x2, y2, type="two.means", na.rm=TRUE)   # should get [1] -0.1875458  0.7320355

# checking the numeric piece
x3 <- c("hi", "how", "are", "you", "?")  
mean_ci(x3)                          # should get an informative error
mean_ci(x3, y2, type = "two.means")  # should get an informative error

# check the type piece
mean_ci(x2, y2, type = "two.groups")  # should get an informative error
```


(2) Write a function called `prop_ci()` for computing either a 95% confidence interval for a single proportion or a 95% confidence interval for the difference in proportions.

```{r}
#Put your code for this here

```


If you would like a way to check that your confidence intervals are correct, here is the code I will use to check that your function works appropriately:
```{r echo = TRUE, eval = FALSE}
set.seed(8675309)
x <- rbinom(50, 1, .5)
y <- rbinom(30, 1, .2)

prop_ci(x)   # should get [1] 0.4196006 0.7003994

prop_ci(x, y, type="two.props")   # should get [1] 0.1978071 0.5888596

# checking the na.rm piece
x2 <- c(x, NA)
y2 <- c(y, NA)
prop_ci(x2, y2, type="two.props")  # should get [1] NA NA or an error message depending on how checked for binary vectors
prop_ci(x2, y2, type="two.props", na.rm=TRUE)   # should get [1] 0.1978071 0.5888596

# checking the binary piece
x3 <- c(3,4,5,2,0,1)
prop_ci(x3)
prop_ci(x3, y2, type = "two.props")

# check the type piece
prop_ci(x2, y2, type = "two.groups")
```

(3) Extra credit: Write a function called `ratio_ci()` for computing either a 95% confidence interval for the odds ratio or a 95% confidence interval for the relative risk between two groups.

```{r}
#Put your code for this here

```

To check your code, I will use the following:
```{r echo = TRUE, eval = FALSE}
ratio_ci(n1 = 20, n2 = 10, p1 = .5, p2 = .7)   # should get [1] 0.08275144 2.21958041
ratio_ci(n1 = 20, n2 = 10, p1 = .5, p2 = .7, type = "odds.ratio")   # should get [1] 0.08275144 2.21958041
ratio_ci(n1 = 20, n2 = 10, p1 = .5, p2 = .7, type = "risk.ratio")   # should get [1] 0.3883215 1.3138702
ratio_ci(n1 = 20, n2 = 10, p1 = .5, p2 = .7, type = "hello")   # should get error message

# checking the proportions check
ratio_ci(n1 = 20, n2 = 10, p1 = .5, p2 = 1.3)   # should get error message
ratio_ci(n1 = 20, n2 = 10, p1 = 1.5, p2 = .3)   # should get error message
ratio_ci(n1 = 20, n2 = 10, p1 = .5, p2 = 1.3, type = "risk.ratio")   # should get error message
ratio_ci(n1 = 20, n2 = 10, p1 = 1.5, p2 = .3, type = "risk.ratio")    # should get error message
ratio_ci(n1 = 20, n2 = 10, p1 = .5, p2 = 1.3, type = "odds.ratio")    # should get error message
ratio_ci(n1 = 20, n2 = 10, p1 = 1.5, p2 = .3, type = "odds.ratio")    # should get error message
```
